---
title: "finalAnalyses"
format: html
editor: visual
toc: true
---

# Set-Up

```{r, results='hide',message=FALSE,warning=FALSE}
library(groundhog)
pkgs <-  c("lmerTest", "ggeffects","r2glmm", "tidyverse","here", "sjPlot", "ggpubr", "wesanderson", "effectsize", "correlation")
groundhog.day <- '2022-07-25'
groundhog.library(pkgs, groundhog.day)
here::i_am("analysis/finalStableAnalyses.qmd")
plotDir <- "/Volumes/Research Project/Trait_TestRetest/WeekTRT/plots/"
```

# Import Data

```{r, results='hide',message=FALSE,warning=FALSE}
fullLong <- as.data.frame( arrow::read_parquet(here("data/longChangeInds.parquet")) ) 
ICCmat <- as.data.frame( arrow::read_parquet(here("data/ICCdf.parquet")) )
```

# Scaling

```{r, results='hide',message=FALSE,warning=FALSE}
fullLong$absDS.Z <- scale(fullLong$absDS)
fullLong$diffScore.Z <- scale(fullLong$diffScore)
fullLong$selfRespT1.Z <- scale(fullLong$selfRespT1)
fullLong$selfRespT2.Z <- scale(fullLong$selfRespT2)
fullLong$outDegree.Z <- scale(fullLong$outDegree)
fullLong$inDegree.Z <- scale(fullLong$inDegree)
fullLong$interpersonal.Z <- scale(fullLong$interpersonal)
fullLong$category.Z <- scale(fullLong$category)
fullLong$desirability.Z <- scale(fullLong$desirability)
fullLong$prevalence.Z <- scale(fullLong$prevalence)
fullLong$observability.Z <- scale(fullLong$observability)
fullLong$SE_C.Z <- scale(fullLong$SE_C)
fullLong$SCC_C.Z <- scale(fullLong$SCC_C)
fullLong$DS_C.Z <- scale(fullLong$DS_C)
fullLong$CESD_C.Z <- scale(fullLong$CESD_C)
fullLong$SWLS_C.Z <- scale(fullLong$SWLS_C)
fullLong$MAIA.All_C.Z <- scale(fullLong$MAIA.All_C)
```

# **Indegree Predicts Less Rank-Order Stability**

```{r}
KT12 <- fullLong %>% group_by(traits) %>% select(selfRespT1, selfRespT2) %>% correlation(method="Kendall")
ST12 <- fullLong %>% group_by(traits) %>% select(selfRespT1, selfRespT2) %>% correlation(method="Spearman")
PT12 <- fullLong %>% group_by(traits) %>% select(selfRespT1, selfRespT2) %>% correlation(method="Pearson")

cor.test(KT12$tau, PT12$r)
cor.test(ST12$rho, PT12$r)
cor.test(ST12$rho, KT12$tau)
```

```{r}
fullLong$subID <- as.factor(fullLong$subID)
PT12 <- fullLong %>% group_by(traits) %>% select(traits, subID, selfRespT1, selfRespT2) %>% correlation(method="Kendall",multilevel = T)

fullLong <- fullLong %>% 
  group_by(subID) %>% 
  mutate(T1.Rank = rank(selfRespT1), T2.Rank = rank(selfRespT2))

fullLong <- fullLong %>% 
  mutate(T1.Rank = rank(selfRespT1), T2.Rank = rank(selfRespT2))

m<-lmer( scale(T2.Rank) ~ scale(T1.Rank) * scale(outDegree) + scale(inDegree) * scale(T1.Rank) + valence + ( scale(T1.Rank) + valence |subID) + (1 | traits), data = fullLong, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))
summary(m)

m<-lmer( (T2.Rank-T1.Rank) ~ scale(outDegree) + scale(inDegree) + valence + ( valence |subID) + (1 | traits), data = fullLong, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))
summary(m)
```

## ICC (R to Z)

```{r}
m <- lm(scale(ICCr2z) ~ scale(outDegree) + scale(inDegree) + valence, data = ICCmat)
eta_squared(m)
tab_model(m, collapse.ci = T, show.stat=T, show.r2 = T, show.se = T, string.pred = c("Fixed Effects"), string.est = "Coef.", string.se = "SE", string.stat = "t", digits = 3, emph.p = F, dv.labels = "Rank-Order Stability", show.df=T)
```

## Correlation

```{r}
m <- lm(scale(RO_Stab.trait) ~ scale(outDegree) + scale(inDegree) + valence, data = ICCmat)
eta_squared(m)
tab_model(m, collapse.ci = T, show.stat=T, show.r2 = T, show.se = T, string.pred = c("Fixed Effects"), string.est = "Coef.", string.se = "SE", string.stat = "t", digits = 3, emph.p = F, dv.labels = "Rank-Order Stability", show.df=T)
```

# Indegree Predicts Less Mean-Level Stability

```{r}
m <- lm(scale(aML_Stab.trait) ~ scale(outDegree) + scale(inDegree) + valence, data = ICCmat)
eta_squared(m)
tab_model(m, collapse.ci = T, show.stat=T, show.r2 = T, show.se = T, string.pred = c("Fixed Effects"), string.est = "Coef.", string.se = "SE", string.stat = "t", digits = 3, emph.p = F, dv.labels = "Mean-Level Stability", show.df=T)
```

```{r}
m <- lm(scale(aML_Stab.trait) ~ scale(outDegree) * scale(inDegree) + valence, data = ICCmat)
eta_squared(m)
tab_model(m, collapse.ci = T, show.stat=T, show.r2 = T, show.se = T, string.pred = c("Fixed Effects"), string.est = "Coef.", string.se = "SE", string.stat = "t", digits = 3, emph.p = F, dv.labels = "Rank-Order Stability", show.df=T)
```

```{r}
m<-lmer(absDS.Z ~ outDegree.Z + valence + inDegree.Z + ( 1 |subID) + (1 | traits), data = fullLong, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))
summary(m)
```

# **Self-Beliefs with More Implications Change Less**

```{r}
m<-lmer(selfRespT2 ~ selfRespT1 * outDegree + valence + outDegree + inDegree + ( 1 |subID) + (1 | traits), data = fullLong, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))
summary(m)
ggpredict(m, c("selfRespT1","outDegree")) %>% plot()
```

```{r}
m<-lmer(absDS.Z ~ outDegree.Z + valence + inDegree.Z + ( valence + outDegree.Z + inDegree.Z |subID) + (1 | traits), data = fullLong, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))
r2beta(m)
```

```{r}
tab_model(m, collapse.ci = T, show.stat=T, show.r2 = T, show.se = T, string.pred = c("Fixed Effects"), string.est = "Coef.", string.se = "SE", string.stat = "t", digits = 3, emph.p = F, dv.labels = "Confidence", df.method = "satterthwaite",show.df=T)
```

# **Self-Beliefs with More Implications Change Less (with covariates)**

```{r}
m<-lmer(absDS.Z ~ outDegree.Z + valence + inDegree.Z + interpersonal.Z + category.Z + observability.Z + prevalence.Z +  ( valence + outDegree.Z + inDegree.Z |subID) + (1 | traits), data = fullLong, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))
```

```{r}
tab_model(m, collapse.ci = T, show.stat=T, show.r2 = T, show.se = T, string.pred = c("Fixed Effects"), string.est = "Coef.", string.se = "SE", string.stat = "t", digits = 3, emph.p = F, dv.labels = "Confidence", df.method = "satterthwaite",show.df=T)
```

# Correlations with ICC

```{r}
cor(ICCmat[c("ICCr2z","absDS","cor","outDegree","inDegree")])
```

# **Individual Differences in Self-Concept Stability as a Function of Outdegree**

## Self-Concept Clarity

```{r}
m<-lmer( absDS.Z ~ SCC_C.Z*outDegree.Z + ( outDegree.Z | subID ) + ( SCC_C.Z | traits), data=fullLong, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))
rb <- r2beta(m)
data.frame(rb$Effect,rb$Rsq)
tab_model(m, collapse.ci = T, show.stat=T, show.r2 = T, show.se = T, string.pred = c("Fixed Effects"), string.est = "Coef.", string.se = "SE", string.stat = "t", digits = 3, emph.p = F, dv.labels = "Evaluation", df.method = "satterthwaite",show.df=T)
```

### Plot

```{r}
m<-lmer( absDS ~ SCC_C*outDegree + ( outDegree | subID ) + ( SCC_C | traits), data= fullLong, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))

p <- ggpredict(m, c("SCC_C","outDegree"))
SCC.outdeg.Stable.Plot <-ggplot(p, aes(x, predicted)) +  geom_line(aes(linetype=group, color=group)) + geom_ribbon(aes(ymin=conf.low, ymax=conf.high, fill=group), alpha=0.15) + scale_linetype_discrete(labels = c("Low Outdegree","Medium Outdegree","High Outdegree")) + scale_color_manual(labels = c("Low Outdegree","Medium Outdegree","High Outdegree"), values = wes_palette("Darjeeling1")) + scale_fill_manual( 
                      labels=c("Low Outdegree","Medium Outdegree","High Outdegree"), values = wes_palette("Darjeeling1")) + theme(
    legend.position = c(.2, .7),
    legend.justification = c("left", "bottom"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6)
    ) + theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold")) + theme(legend.text = element_text(size=12)) + theme(panel.border = element_rect(colour = "black", fill = NA, size =1)) + theme(legend.title = element_blank()) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  xlab("Self-Concept Clarity") + ylab("Absolute Change")
SCC.outdeg.Stable.Plot

ggpredict(m, c("SCC_C","outDegree")) %>% plot(add.data=T) + labs(title="Raw Data",x="Self-Concept Clarity",y="Change")
```

## Self-Esteem

```{r}
m<-lmer( absDS.Z ~ SE_C.Z*outDegree.Z + ( outDegree.Z | subID ) + ( SE_C.Z | traits), data=fullLong, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))
rb <- r2beta(m)
data.frame(rb$Effect,rb$Rsq)
tab_model(m, collapse.ci = T, show.stat=T, show.r2 = T, show.se = T, string.pred = c("Fixed Effects"), string.est = "Coef.", string.se = "SE", string.stat = "t", digits = 3, emph.p = F, dv.labels = "Evaluation", df.method = "satterthwaite",show.df=T)
```

### Plot

```{r}
m<-lmer( absDS ~ SE_C*outDegree + ( outDegree | subID ) + ( SE_C | traits), data= fullLong, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))

p <- ggpredict(m, c("SE_C","outDegree"))
SE.outdeg.Stable.Plot <-ggplot(p, aes(x, predicted)) +  geom_line(aes(linetype=group, color=group)) + geom_ribbon(aes(ymin=conf.low, ymax=conf.high, fill=group), alpha=0.15) + scale_linetype_discrete(labels = c("Low Outdegree","Medium Outdegree","High Outdegree")) + scale_color_manual(labels = c("Low Outdegree","Medium Outdegree","High Outdegree"), values = wes_palette("Darjeeling1")) + scale_fill_manual( 
                      labels=c("Low Outdegree","Medium Outdegree","High Outdegree"), values = wes_palette("Darjeeling1")) + theme(
    legend.position = c(.2, .10),
    legend.justification = c("left", "bottom"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6)
    ) + theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold")) + theme(legend.text = element_text(size=12)) + theme(panel.border = element_rect(colour = "black", fill = NA, size =1)) + theme(legend.title = element_blank()) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  xlab("Self-Esteem") + ylab("Absolute Change")
SE.outdeg.Stable.Plot

ggpredict(m, c("SE_C","outDegree")) %>% plot(add.data=T) + labs(title="Raw Data",x="Self-Esteem",y="Change")
```

## Dialectical Self-Views

```{r}
m<-lmer( absDS.Z ~ DS_C.Z*outDegree.Z + ( outDegree.Z | subID ) + ( DS_C.Z | traits), data=fullLong, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))
rb <- r2beta(m)
data.frame(rb$Effect,rb$Rsq)
tab_model(m, collapse.ci = T, show.stat=T, show.r2 = T, show.se = T, string.pred = c("Fixed Effects"), string.est = "Coef.", string.se = "SE", string.stat = "t", digits = 3, emph.p = F, dv.labels = "Evaluation", df.method = "satterthwaite",show.df=T)
```

### Plot

```{r}
m<-lmer( absDS ~ DS_C*outDegree + ( outDegree | subID ) + ( DS_C | traits), data= fullLong, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))

p <- ggpredict(m, c("DS_C","outDegree"))
DS.outdeg.Stable.Plot <-ggplot(p, aes(x, predicted)) +  geom_line(aes(linetype=group, color=group)) + geom_ribbon(aes(ymin=conf.low, ymax=conf.high, fill=group), alpha=0.15) + scale_linetype_discrete(labels = c("Low Outdegree","Medium Outdegree","High Outdegree")) + scale_color_manual(labels = c("Low Outdegree","Medium Outdegree","High Outdegree"), values = wes_palette("Darjeeling1")) + scale_fill_manual( 
                      labels=c("Low Outdegree","Medium Outdegree","High Outdegree"), values = wes_palette("Darjeeling1")) + theme(
    legend.position = c(.5, .70),
    legend.justification = c("left", "bottom"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6)
    ) + theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold")) + theme(legend.text = element_text(size=12)) + theme(panel.border = element_rect(colour = "black", fill = NA, size =1)) + theme(legend.title = element_blank()) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  xlab("Dialectical Self-Views") + ylab("Absolute Change")
DS.outdeg.Stable.Plot

ggpredict(m, c("DS_C","outDegree")) %>% plot(add.data=T) + labs(title="Raw Data",x="Dialectical Self-Views",y="Change")
```

## Depressive Symptoms

```{r}
m<-lmer( absDS.Z ~ CESD_C.Z*outDegree.Z + ( outDegree.Z | subID ) + ( SWLS_C.Z | traits), data=fullLong, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))
rb <- r2beta(m)
data.frame(rb$Effect,rb$Rsq)
tab_model(m, collapse.ci = T, show.stat=T, show.r2 = T, show.se = T, string.pred = c("Fixed Effects"), string.est = "Coef.", string.se = "SE", string.stat = "t", digits = 3, emph.p = F, dv.labels = "Evaluation", df.method = "satterthwaite",show.df=T)
```

### Plot

```{r}
m<-lmer( absDS ~ CESD_C*outDegree + ( outDegree | subID ) + ( CESD_C | traits), data= fullLong, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))

p <- ggpredict(m, c("CESD_C","outDegree"))
CESD.outdeg.Stable.Plot <-ggplot(p, aes(x, predicted)) +  geom_line(aes(linetype=group, color=group)) + geom_ribbon(aes(ymin=conf.low, ymax=conf.high, fill=group), alpha=0.15) + scale_linetype_discrete(labels = c("Low Outdegree","Medium Outdegree","High Outdegree")) + scale_color_manual(labels = c("Low Outdegree","Medium Outdegree","High Outdegree"), values = wes_palette("Darjeeling1")) + scale_fill_manual( 
                      labels=c("Low Outdegree","Medium Outdegree","High Outdegree"), values = wes_palette("Darjeeling1")) + theme(
    legend.position = c(.55, .10),
    legend.justification = c("left", "bottom"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6)
    ) + theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold")) + theme(legend.text = element_text(size=12)) + theme(panel.border = element_rect(colour = "black", fill = NA, size =1)) + theme(legend.title = element_blank()) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  xlab("Depressive Symptoms") + ylab("Absolute Change")
CESD.outdeg.Stable.Plot

ggpredict(m, c("CESD_C","outDegree")) %>% plot(add.data=T) + labs(title="Raw Data",x="Depressive Symptoms",y="Change")
```

## Satisfaction with Life

```{r}
m<-lmer( absDS.Z ~ SWLS_C.Z*outDegree.Z + ( outDegree.Z | subID ) + ( SWLS_C.Z | traits), data=fullLong, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))
rb <- r2beta(m)
data.frame(rb$Effect,rb$Rsq)
tab_model(m, collapse.ci = T, show.stat=T, show.r2 = T, show.se = T, string.pred = c("Fixed Effects"), string.est = "Coef.", string.se = "SE", string.stat = "t", digits = 3, emph.p = F, dv.labels = "Evaluation", df.method = "satterthwaite",show.df=T)
```

### Plot

```{r}
m<-lmer( absDS ~ SWLS_C*outDegree + ( outDegree | subID ) + ( SWLS_C | traits), data= fullLong, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))

p <- ggpredict(m, c("SWLS_C","outDegree"))
SWLS.outdeg.Stable.Plot <-ggplot(p, aes(x, predicted)) +  geom_line(aes(linetype=group, color=group)) + geom_ribbon(aes(ymin=conf.low, ymax=conf.high, fill=group), alpha=0.15) + scale_linetype_discrete(labels = c("Low Outdegree","Medium Outdegree","High Outdegree")) + scale_color_manual(labels = c("Low Outdegree","Medium Outdegree","High Outdegree"), values = wes_palette("Darjeeling1")) + scale_fill_manual( 
                      labels=c("Low Outdegree","Medium Outdegree","High Outdegree"), values = wes_palette("Darjeeling1")) + theme(
    legend.position = c(.2, .10),
    legend.justification = c("left", "bottom"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6)
    ) + theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold")) + theme(legend.text = element_text(size=12)) + theme(panel.border = element_rect(colour = "black", fill = NA, size =1)) + theme(legend.title = element_blank()) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  xlab("Satisfaction with Life") + ylab("Absolute Change")
SWLS.outdeg.Stable.Plot

ggpredict(m, c("SWLS_C","outDegree")) %>% plot(add.data=T) + labs(title="Raw Data",x="Satisfaction with Life",y="Change")
```

## Interoceptive Awareness

```{r}
m<-lmer( absDS.Z ~ MAIA.All_C.Z*outDegree.Z + ( outDegree.Z | subID ) + ( SWLS_C.Z | traits), data=fullLong, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))
rb <- r2beta(m)
data.frame(rb$Effect,rb$Rsq)
tab_model(m, collapse.ci = T, show.stat=T, show.r2 = T, show.se = T, string.pred = c("Fixed Effects"), string.est = "Coef.", string.se = "SE", string.stat = "t", digits = 3, emph.p = F, dv.labels = "Evaluation", df.method = "satterthwaite",show.df=T)
```

### Plot

```{r}
m<-lmer( absDS ~ MAIA.All_C*outDegree + ( outDegree | subID ) + ( MAIA.All_C | traits), data= fullLong, control=lmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5)))

p <- ggpredict(m, c("MAIA.All_C","outDegree"))
MAIA.All.outdeg.Stable.Plot <-ggplot(p, aes(x, predicted)) +  geom_line(aes(linetype=group, color=group)) + geom_ribbon(aes(ymin=conf.low, ymax=conf.high, fill=group), alpha=0.15) + scale_linetype_discrete(labels = c("Low Outdegree","Medium Outdegree","High Outdegree")) + scale_color_manual(labels = c("Low Outdegree","Medium Outdegree","High Outdegree"), values = wes_palette("Darjeeling1")) + scale_fill_manual( 
                      labels=c("Low Outdegree","Medium Outdegree","High Outdegree"), values = wes_palette("Darjeeling1")) + theme(
    legend.position = c(.2, .07),
    legend.justification = c("left", "bottom"),
    legend.box.just = "left",
    legend.margin = margin(6, 6, 6, 6)
    ) + theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold")) + theme(legend.text = element_text(size=12)) + theme(panel.border = element_rect(colour = "black", fill = NA, size =1)) + theme(legend.title = element_blank()) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  xlab("Interoceptive Awareness") + ylab("Absolute Change")
MAIA.All.outdeg.Stable.Plot

ggpredict(m, c("MAIA.All_C","outDegree")) %>% plot(add.data=T) + labs(title="Raw Data",x="Interoceptive Awareness",y="Change")
```

```{r}
ggarrange(SE.outdeg.Stable.Plot, SCC.outdeg.Stable.Plot, CESD.outdeg.Stable.Plot, nrow=1, ncol=3, common.legend = T)
ggsave(paste0(plotDir,"IndDiff.outdegStable",".png"), width = 13, height = 7.5, units = "in")
ggsave(paste0(plotDir,"IndDiff.outdegStable",".tiff"), width = 13, height = 7.5, units = "in")
```

# 
